Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
fix figure 1 and 2
changes to some figures

% \begin{figure}[t!]
% 	\centering
% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
% 	\label{fig:teaser}
% \end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
	\caption{Biological constraints for 3D segments in Connectomics.}
	\label{fig:biological_constraints}
\end{figure}

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For the region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if that is the case for larger volumes.
\TODO{sth. about figure 1.}

%\TODO{the selling point is to add biological constraint}
%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b).
This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser_pipeline}c).

>>>>

% \begin{figure}[t!]
% 	\centering
% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
% 	\label{fig:teaser}
% \end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v3.png}
	\caption{Biological constraints for 3D segments in Connectomics.}
	\label{fig:biological_constraints}
\end{figure}

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For the region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if that is the case for larger volumes.

%\TODO{the selling point is to add biological constraint}
%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes (Fig.~\ref{fig:biological_constraints}).
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b).
This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser_pipeline}c).

### 2018-03-14 papers/eccv2018/4_results.tex
changes to some figures

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}		\includegraphics[width=0.45\linewidth]{./figures/precision-and-recall.png}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
	\label{fig:receiver-operating-characteristic}
\end{figure}

>>>>

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--1.png}
	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--2.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
	\label{fig:receiver-operating-characteristic}
\end{figure}
